### 2019-01-02 revisions/review-responses.tex

        %--------------------------------------------------------------------

        \question  What are the main differences of this work with the previous 
        works, especially with the work published by Park at al. in ``Whole core 
        analysis of molten salt breeder reactor with online fuel reprocessing''?
        \begin{solution}
                Thank you for your question. The new paragraph has been added:

                The works described in \cite{park_whole_2015} and 
                \cite{jeong_equilibrium_2016} are most similar to the work 
                presented in this paper. However, few major differences worse to 
                be mentioned: (1) Park \emph{et al.} employed MCNP6 for depletion 
				simulations while SERPENT2 was used in this work (SERPENT2 seems 
				to be much faster in massively parallel simulations involving more 
				than 1000 cores); (2) full-core reactor model herein is more 
				detailed and has no major approximation comparing with Park \emph{et al.}
				(detailed full-core models comparison might be found elsewhere
				\cite{rykhlevskii_full-core_2017}); (3) Park \emph{et al.} and 
				Jeong \emph{et al.} both considered volatile gases, noble metals 
				removal and $^{233}$Pa separation while in the current work we are 
				implemented detailed reprocessing scheme described in conceptual 
				MSBR design \cite{robertson_conceptual_1971}; (4) $^{232}$Th 
				neutron capture reaction rate has been investigated to prove 
				advantages of two-region core design; (5) the effect of removing 
				fission product removal from fuel salt has been studied. 
        \end{solution}

        %--------------------------------------------------------------------
        \question  How did the authors verify the coupled SaltProc and Serpent 
        code system?  
        \begin{solution}
                We have compared few parameters (multiplication factor, Th refill 
                rate, neutron energy spectrum) with Betzler \emph{et al.} 											\cite{betzler_molten_2017} and mentioned it in the Result section. 
                We also compared neutron energy spectrum and temperature coefficients
                 for equilibrium composition with Park \emph{et al.} \cite{park_whole_2015}.
                In a future SaltProc release suite of unit tests will be added 
                to make sure that results are consistent with our test cases.
        \end{solution}

@@

        %--------------------------------------------------------------------
        \question  In Page 10, ``SERPENT generates the problem-dependent nuclear 
        data library'', how did SERPENT generate the problem-dependent nuclear 
        data library? What kind of nuclear data library did SERPENT generate?
        \begin{solution}
                Thank you for your kind review. The statement has been removed
		        entirely and we emphasized that temperature of each material is 
		        assumed to be constant over 60 years:

		        The specific temperature was fixed for each material and did 
		        not change during the reactor operation. 
        \end{solution}

        %--------------------------------------------------------------------
        \question  In Page 14, ``depletioncalculations'' should be ``depletion 
        calculations''.
        \begin{solution}
                Thanks for catching this, fixed.
        \end{solution}

        %--------------------------------------------------------------------
        \question  In Page 21, it looks like the neutron spectrum is not 
        normalized in Figure 10. It is recommended to normalize the neutron 
        spectrum for comparison.
        \begin{solution}
                Thank you for the comment. Neutron energy spectrum in Figure 
                10 and 11 are normalized per unit lethargy and the area under 
                the curve is normalized to 1.
        \end{solution}

### 2019-01-03 revisions/review-responses.tex

        %---------------------------------------------------------------------
        \question  Table 1, page 3: SCALE/TRITON is fast as well as thermal 
        reactor capable.  
        \begin{solution}
		        Thank you for the recommendation. In Table 1 ``thermal'' has been changed 
		        to ``thermal/fast''.
        \end{solution}

        %---------------------------------------------------------------------
        \question  Page 4, Line 48: Should read ``...and refill using a single 
        or multiple unit cell ....''
        \begin{solution}
        		That statement has been modified as requested.
        \end{solution}

        %---------------------------------------------------------------------
        \question  Page 4, Line 55. Also worth noting that the latest SCALE 
        release will have the same functionality using continuous removal (B. 
        R. Betzler, J. J. Powers, N. R. Brown, and B. T. Rearden, ``Molten Salt 
        Reactor Neutronics Tools in SCALE,'' Proc. M\&C 2017 - International 
        Conference on Mathematics \& Computational Methods Applied to Nuclear 
        Science and Engineering, Jeju, Korea, Apr. 16-20 (2017).)
        \begin{solution}
		        Thank you for the update. This sentence has been added:

		        The latest SCALE release will also have the same functionality using 
        		truly continuous removals \cite{betzler_implementation_2017}.
        \end{solution}

@@

        %---------------------------------------------------------------------
        \question  Page 18, Figure 7: The figure is hard to interpret or see 
        clearly what is going on. Could an additional figure or a zoomed in 
        portion be added to show what the swing in k is over a much shorter 
        time interval? k seems to be swinging dramatically but over what time 
        period and how would this be controlled in reality? The graph almost 
        suggests that the core is unstable??
        \begin{solution}
                <++>
        \end{solution}

        %---------------------------------------------------------------------
        \question  Page 18, line 327: Are those elements removed every 3435 
        days, or is it that the entire salt core is discharged?
        \begin{solution}
		        100 \% of those elements atoms removed every 3435 days. Full salt discard
		         as it mentioned in Table 3 has not been implemented. More detailed 
		         explanation of this has been added:

		        Additionally, the presence of rubidium, strontium, cesium, and barium in
		         the core are disadvantageous to reactor physics. In fact, SaltProc fully 
		         removes all these elements every 3435 days (not a small mass fraction 
		         every 3 days) which causes the multiplication factor to jump by 
		        approximately 450 pcm, and limits using the batch approach for online 
		        reprocessing simulations. In future versions of SaltProc this drawback 
		        will be eliminated by removing elements with longer cycle times (seminoble 
		        metals, volatile fluorides, Rb, Sr, Cs, Ba, Eu) using different approach. 
		        Only mass fraction (calculated separately for each reprocessing group) 
		        will be removed every depletion step (e.g. 3 days) instead of removing 
		        100\% of element atoms after cycle time. 
        \end{solution}

        %---------------------------------------------------------------------
        \question  Page 19, Figure 8 (and same for Fig 9): y-axis in grams/kgs 
        or mass units would be better for the reader.
        \begin{solution}
                Thank you for the recommendation. Atom density was chosen for publication-to-						publication comparison (e.g. Park \emph{et al.} and Betzler \emph{et al.}
                \cite{park_whole_2015, betzler_molten_2017}). Although mass would certainly 
                be more understandable for the reader and will be added in a future releases.
        \end{solution}

@@

                It must be noted that for the reactor with only thorium feed, 
                at near equilibrium state, the thorium consumption rate is 
				determined by the reactor power, the energy released per fission, 
				and neutron energy spectrum.
        \end{solution}

        %---------------------------------------------------------------------

        \question Are you considering the effect of the gradual poisoning of 
        the graphite with fission products? If not, it would be worthwhile 
        briefly discussing its effect.
        \begin{solution}
                This passage has been added:

				$^{135}$Xe is a strong poison to the reactor, and some 
				fraction of this gas is absorbed by graphite during MSBR
				operation. ORNL calculations shown that for unsealed commercial 
				graphite with helium permeability 10$^{-5}$ cm$^2$/s the 
				calculated poison fraction is less than 2\% \cite{robertson_conceptual_1971}. 
				This parameter can be improved by using experimental graphites 
				or by applying sealing technology. The effect of the gradual 
				poisoning of the core graphite with xenon is not treated here.
        \end{solution}

### 2019-01-03 revisions/review-responses.tex

% \biboptions{}

% Katy Huff addtions
\usepackage{xspace}
\usepackage{color}

\usepackage{multirow}
\usepackage[hyphens]{url}

%\usepackage[acronym,toc]{glossaries}
%\include{acros}

%\makeglossaries

@@

		        Protactinium presents a challenge, since it has a large absorption cross 
				section in the thermal energy spectrum. Moreover, $^{233}$Pa left in the core
				 would produce $^{234}$Pa and $^{234}$U, which both are not useful as fuel, 
				and smaller amount of $^{233}$Pa would decays into the fissile $^{233}$U.
				Accordingly, $^{233}$Pa is continuously 
				removed from the fuel salt into a protactinium decay tank to allow $^{233}$Pa 
				to decay to $^{233}$U without negative impact on neutronics.
        \end{solution}

        %---------------------------------------------------------------------
        \question  Table 3: ``cycle time'' is not defined in the paper. Please 
        add.
        \begin{solution}
		        The ``cycle time'' definition has been added in a first appearance in text.
        \end{solution}

        %---------------------------------------------------------------------
        \question  Page 14, line 224. The 3 day time step as the ``optimum'' for 
        Th fuel cycles in an MSR was first described and concluded by Powers et 
        al. Please add a reference to their initial work.
        \begin{solution}
        		The reference to \cite{powers_new_2013} has been added.
        \end{solution}

        %---------------------------------------------------------------------
        \question  Page 14, line 234 onwards: Doesn't SERPENT already have an 
        MSR removal capability? If so, what is different about using SaltProc 
        with SERPENT?
        \begin{solution}
                It does. We tried use it before but these capabilities needs 
                to be verified. Additional text to clarify this point has 
                been add to solution for question 21.                
        \end{solution}

@@

		        Additionally, the presence of rubidium, strontium, cesium, and barium in
		         the core are disadvantageous to reactor physics. In fact, SaltProc fully 
		         removes all these elements every 3435 days (not a small mass fraction 
		         every 3 days) which causes the multiplication factor to jump by 
		        approximately 450 pcm, and limits using the batch approach for online 
		        reprocessing simulations. In future versions of SaltProc this drawback 
		        will be eliminated by removing elements with longer cycle times (seminoble 
		        metals, volatile fluorides, Rb, Sr, Cs, Ba, Eu) using different approach. 
		        Only mass fraction (calculated separately for each reprocessing group) 
		        will be removed every depletion step (e.g. 3 days) instead of removing 
		        100\% of element atoms after cycle time. 
        \end{solution}

        %---------------------------------------------------------------------
        \question  Page 19, Figure 8 (and same for Fig 9): y-axis in grams/kgs 
        or mass units would be better for the reader.
        \begin{solution}
                Thank you for the recommendation. Atom density was chosen for publication-to-						publication comparison (e.g. Park \emph{et al.} and Betzler \emph{et al.}
                \cite{park_whole_2015, betzler_molten_2017}). Although mass would certainly 
                be more understandable for the reader and will be added in a future releases.
        \end{solution}

        %---------------------------------------------------------------------
        \question  Page 20, Fig 9: What are the wiggles and dips , especially 
        seen for Np235?
        \begin{solution}
		        Explanation of this phenomena has been added as follows:

		         Small dips in neptunium and plutonium number density every 16 years are 
		         caused by removing $^{237}$Np, $^{242}$Pu (included in Processing group 
		         ``Higher nuclides'', see Table 3) which decays
        		  into $^{235}$Np, $^{239}$Pu, respectively. 
        \end{solution}

@@

        %---------------------------------------------------------------------

        \section*{Reviewer 2}

        %---------------------------------------------------------------------

        \question The most critical point of the work is that the built-in 
        capabilities for online reprocessing of Serpent 2 have not been used. 
        Their use is mentioned in the future work, but it is not clear why 
        these capabilities have not been used in the current work. To the 
        author's knowledge, they have been available in Serpent 2 since quite a 
        while. The authors should clarify this point at the beginning of the 
        paper, and not only in the ``Future work'' section. Even though the 
        technical work was done without using these capabilities, they should 
        highlight what  SaltProc adds to the built-in Serpent capabilities, and 
        they should at least try to extrapolate on the potential advantages of 
        combining  SaltProc and Serpent capabilities. Based on this, they 
        should slightly restructure the paper in order to prove the claimed 
        advantages over Serpent 2.
        \begin{solution}
                Thank you for your kind review. We tried to use these capabilities 
                \cite{rykhlevskii_online_2017} but have had number of issues which 
                are hard to resolve due to lack of documentation and publications 
                involving this feature. Following paragraph has been added to 
                clarify why these capabilities have not been used in current work:

                We employed this extended SERPENT2 for a simplified unit-cell 
                geometry of thermal spectrum thorium-fueled MSBR and have had 
                following problems: (1) lack of documentation describing how 
                to use this built-in SERPENT2 online reprocessing capabilities
                \footnote{ Some challenges in no particular order: mass 
                conservation is hard to achieve; not clear when use mflow card 
                type 0, 1 or 2; difference between CRAM and TTA results; etc.} 
				(Discussion forum for SERPENT users is only useful 
				source of information at the moment); (2) reactivity control 
				module described in Aufiero \emph{et al.} is not available 
				in the latest SERPENT 2.1.30 release; (3) infinite multiplication 
				factor behavior for simplified unit-cell model obtained using 
				SERPENT2 built-in capabilities \cite{rykhlevskii_online_2017} 
				does not match with exist MCNP6/Python-script results for the 
				similar model by Jeong and Park\footnote{ In our study 
				k$_{\infty}$ drops from 1.05 to 1.005 during a 1200 days of 
				depletion simulation while in Jeong and Park work this parameter 
				decreasing slowly from 1.065 to 1.05 for the 
				similar time-frame.} \cite{jeong_equilibrium_2016}; (4) only few 
				publication \cite{aufiero_extended_2013, ashraf_nuclear_2018} 
				using these capabilities are available which is indicative of 
				lack of reproducibility. Nevertheless, truly continuous 
				online reprocessing capabilities of SERPENT2 is desirable feature 
				for our future research. However, these capabilities should be 
				carefully verified against ChemTriton/SCALE or proposed 
				SaltProc/SERPENT2 package, and could be employed 
				for removal of fission products with shorter residence time 
				(e.g., Xe, Kr) which have a strong negative impact on core 
				lifetime and breeding efficiency which we intent to do in 
				the nearest future.
        \end{solution}

@@

        %--------------------------------------------------------------------
        \question  How did the authors verify the coupled SaltProc and Serpent 
        code system?  
        \begin{solution}
                We have compared few parameters (multiplication factor, Th refill 
                rate, neutron energy spectrum) with Betzler \emph{et al.} 											\cite{betzler_molten_2017} and mentioned it in the Result section. 
                We also compared neutron energy spectrum and temperature coefficients
                 for equilibrium composition with Park \emph{et al.} \cite{park_whole_2015}.
                In a future SaltProc release suite of unit tests will be added 
                to make sure that results are consistent with our test cases.
        \end{solution}

        %--------------------------------------------------------------------
        \question  In Page 3, the title of ``Table 1'' should not only contain 
        the ``fast spectrum system''. The work published by Zhou and Yang et al. 
        with the title of ``Fuel cycle analysis of molten salt reactors based on 
        coupled neutronics and thermal-hydraulics calculations'' needs to be 
        included in Table 1 for completeness.
        \begin{solution}
                Thank you for your excellent recommendations. The table has been 
                enriched as requested.
        \end{solution}

        %--------------------------------------------------------------------
        \question  In Page 5, the following sentence needs to be explained. ``We 
        employed this extended SERPENT 2 for a simplified unit-cell geometry of 
        thermal spectrum thorium-fueled MSBR and obtained results which 
        contradict existing MSBR depletion simulations.''
        \begin{solution}
                This statement has been significantly extended (see Solution 21).
        \end{solution}

### 2019-01-03 conclusion.tex
Reviewer #1: Pa removal reasons and cycle time footnote added #32
Reviewer 2 minor comments mostly resolved #39
Explanation why SERPENT2 online feature doesn't used added #34

This work introduces the open source \gls{MSR} simulation package SaltProc. 
SaltProc expands the capability of SERPENT 2, the continuous-energy Monte Carlo 
code to include online reprocessing in liquid-fueled \gls{MSR} operation 
\cite{andrei_rykhlevskii_arfc/saltproc:_2018}. Benefits of SaltProc include 
generic geometry modeling, multi-flow capabilities, time-dependent feed and 
removal rates, and the ability to specify removal efficiency. The main goal of 
this work has 
been to demonstrate SaltProc's capability to find the equilibrium fuel salt 
composition (where equilibrium is defined as when the number densities of major 
isotopes vary by less than 1\% over several years). A secondary goal has been to 
compare predicted operational and safety parameters (e.g., neutron energy 
spectrum, power and breeding distribution, temperature coefficients of 
reactivity) of the \gls{MSBR} at startup and equilibrium state. A tertiary goal 
has been to demonstrate benefits of continuous fission products removal for 
thermal \gls{MSR} design.

@@

\subsection{Equilibrium state search}
The results of this study indicate that the effective multiplication factor 
slowly decreases from 1.075 and reaches 1.02 at equilibrium after approximately 
6 years of operation. At the same time, the concentrations of $^{233}$U, $^{232}$Th, 
$^{233}$Pa, $^{232}$Pa stabilized after approximately 2500 days of operation. 
Particularly, $^{233}$U number density equilibrates\footnote{fluctuates less 
than 0.8\%} after 16 years of operation. Consequently, the core reaches the quasi-equilibrium state 
after 16 years of operation. However, a wide variety of nuclides, 
including fissile isotopes (e.g. $^{233}$U, $^{239}$Pu) and non-fissile strong 
absorbers (e.g. $^{234}$U), continue accumulating in the core. The current work results 
show that a true equilibrium composition cannot exist but balance
between strong absorber accumulation and new fissile material 
production can be achieved to keep the reactor critical.

@@

Only the batch-wise online reprocessing approach has been treated in this 
work. However, the SERPENT 2 Monte Carlo code was recently extended for 
continuous online fuel reprocessing simulation \cite{aufiero_extended_2013}. 
This extension must be verified against existing SaltProc/SERPENT or 
ChemTriton/SCALE packages, and could be employed for immediate removal of 
fission product gases (e.g., Xe, Kr) which have a strong negative impact on 
core lifetime and breeding efficiency. Finally, using the built-in SERPENT 2 
Monte Carlo code online reprocessing \& refueling material burnup routine would 
significantly speed up computer-intensive full-core depletion simulations.

>>>>

This work introduces the open source \gls{MSR} simulation package SaltProc. 
SaltProc expands the capability of SERPENT 2, the continuous-energy Monte Carlo 
code to include online reprocessing in liquid-fueled \gls{MSR} operation 
\cite{rykhlevskii_arfc/saltproc:_2018}. Benefits of SaltProc include 
generic geometry modeling, multi-flow capabilities, time-dependent feed and 
removal rates, and the ability to specify removal efficiency. The main goal of 
this work has 
been to demonstrate SaltProc's capability to find the equilibrium fuel salt 
composition (where equilibrium is defined as when the number densities of major 
isotopes vary by less than 1\% over several years). A secondary goal has been to 
compare predicted operational and safety parameters (e.g., neutron energy 
spectrum, power and breeding distribution, temperature coefficients of 
reactivity) of the \gls{MSBR} at startup and equilibrium state. A tertiary goal 
has been to demonstrate benefits of continuous fission products removal for 
thermal \gls{MSR} design.

@@

\subsection{Equilibrium state search}
The results of this study indicate that the effective multiplication factor 
slowly decreases from 1.075 and reaches 1.02 at equilibrium after approximately 
6 years of operation. At the same time, the concentrations of $^{233}$U, $^{232}$Th, 
$^{233}$Pa, $^{232}$Pa stabilized after approximately 2500 days of operation. 
Particularly, $^{233}$U number density equilibrates\footnote{fluctuates less 
than 0.8\%} after 16 years of operation. Consequently, the core reaches the quasi-equilibrium state after 16 years of operation. However, a wide variety of nuclides, 
including fissile isotopes (e.g. $^{233}$U, $^{239}$Pu) and non-fissile strong 
absorbers (e.g. $^{234}$U), continue accumulating in the core. %The current work results 
%show that a true equilibrium composition cannot exist but balance
%between strong absorber accumulation and new fissile material 
%production can be achieved to keep the reactor critical.

@@

Only the batch-wise online reprocessing approach has been treated in this 
work. However, the SERPENT 2 Monte Carlo code was extended for 
continuous online fuel reprocessing simulation \cite{aufiero_extended_2013}. 
This extension must be verified against existing SaltProc/SERPENT or 
ChemTriton/SCALE packages, and could be employed for immediate removal of 
fission product gases (e.g., Xe, Kr) which have a strong negative impact on 
core lifetime and breeding efficiency. Finally, using the built-in SERPENT 2 
Monte Carlo code online reprocessing \& refueling material burnup routine would 
significantly speed up computer-intensive full-core depletion simulations.

### 2019-01-03 introduction.tex
Explanation why SERPENT2 online feature doesn't used added #34

\begin{table}[ht!]
\caption{Tools and methods for \glspl{MSR} fuel cycle analysis.}
\begin{tabularx}{\textwidth}{ m | b | x } 
\hline Neutronic code    & \qquad Authors & Spectrum   \\
\hline
\gls{MCNP}/REM \cite{noauthor_mcnp_2004,heuer_simulation_2010}  & Doligez 
\emph{et al.}, 2014; Heuer \emph{et al.}, 2014  
\cite{doligez_coupled_2014,heuer_towards_2014}    & fast \\
\hline
ERANOS \cite{ruggieri_eranos_2006}  & Fiorina \emph{et al.}, 2013 
\cite{fiorina_investigation_2013}            & fast \\
\hline
KENO-IV/ORIGEN \cite{goluoglu_monte_2011,gauld_isotopic_2011}     & Sheu 
\emph{et al.}, 2013 \cite{sheu_depletion_2013} & fast \\
\hline
SERPENT 2 \cite{leppanen_serpent_2015}  & Aufiero \emph{et al.}, 2013 
\cite{aufiero_extended_2013} & fast \\
\hline
DIF3D \cite{derstine_dif3d:_1984} & Zhou \emph{et al.}, 2018 
\cite{zhou_fuel_2018} & thermal/ fast \\
\hline
MCODE/ORIGEN2 \cite{xu_mcode_2008,croff_users_1980}      & Ahmad \emph{et al.}, 
2015 \cite{ahmad_neutronics_2015}   & thermal  \\
\hline
\gls{MCNP}6/CINDER90 \cite{goorley_mcnp6_2013}     & Park \emph{et al.}, 2015; 
Jeong \emph{et al.}, 2016 \cite{park_whole_2015, jeong_equilibrium_2016}& 
thermal\\
\hline
SCALE/TRITON \cite{bowman_scale_2011,powers_new_2013}    & Powers \emph{et al.}, 
2014; Betzler \emph{et al.}, 2017 
\cite{powers_new_2013,powers_inventory_2014,betzler_molten_2017}& thermal/ fast\\
\hline
SERPENT 2     & Rykhlevskii \emph{et al.}, 2017 \cite{rykhlevskii_online_2017} & 
thermal\\
\hline
\gls{MCNP}/REM  & Nuttin \emph{et al.} \cite{nuttin_potential_2005}&thermal  \\ 
\hline
\end{tabularx}
  \label{tab:fs_codes}
\end{table}
\FloatBarrier

@@

Aufiero \emph{et al.} extended the Monte Carlo burnup code SERPENT 2 and 
employed it to study the material isotopic evolution of the 
\gls{MSFR}\cite{aufiero_extended_2013}. The 
developed extension directly accounts for the effects of online fuel 
reprocessing on depletion calculations and features a reactivity control 
algorithm. The extended version of SERPENT 2 was assessed against a dedicated 
version of the deterministic ERANOS-based EQL3D procedure 
\cite{ruggieri_eranos_2006} and adopted to analyze the \gls{MSFR} fuel salt 
isotopic evolution. We employed this extended SERPENT 2 for a simplified 
unit-cell geometry of thermal spectrum thorium-fueled \gls{MSBR} and obtained 
results which contradict existing \gls{MSBR} depletion simulations 
\cite{jeong_equilibrium_2016}.

The present work introduces the online reprocessing simulation package, SaltProc, 
which expands the capability of the continuous-energy Monte Carlo Burnup 
calculation code, SERPENT 2 \cite{leppanen_serpent_2015}, for simulation 
liquid-fueled \gls{MSR} operation 
\cite{rykhlevskii_arfc/saltproc:_2018}. It also reports the 
application of the coupled SaltProc-SERPENT 2 system to the \gls{MSBR}, an 
extension of the work presented in 
\cite{rykhlevskii_full-core_2017, rykhlevskii_online_2017}. In this work, we 
analyzed \gls{MSBR} neutronics and fuel cycle to establish its equilibrium core 
composition. Additionally, we compared predicted operational and safety parameters of the \gls{MSBR} at 
both the initial and equilibrium states to characterize the evolution of its 
safety case over time. Finally, these simulations determined the appropriate $^{232}$Th feed rate  
for maintaining criticality and enabled analysis of the overall \gls{MSBR} fuel 
cycle performance.

>>>>

\begin{table}[ht!]
\caption{Tools and methods for \glspl{MSR} fuel cycle analysis.}
\begin{tabularx}{\textwidth}{ m | b | x } 
\hline Neutronic code    & \qquad Authors & Spectrum   \\
\hline
\gls{MCNP}/REM \cite{noauthor_mcnp_2004,heuer_simulation_2010}  & Doligez 
\emph{et al.}, 2014; Heuer \emph{et al.}, 2014  
\cite{doligez_coupled_2014,heuer_towards_2014}    & fast \\
\hline
ERANOS \cite{ruggieri_eranos_2006}  & Fiorina \emph{et al.}, 2013 
\cite{fiorina_investigation_2013}            & fast \\
\hline
KENO-IV/ORIGEN \cite{goluoglu_monte_2011,gauld_isotopic_2011}     & Sheu 
\emph{et al.}, 2013 \cite{sheu_depletion_2013} & fast \\
\hline
SERPENT2 \cite{leppanen_serpent_2015}  & Aufiero \emph{et al.}, 2013 
\cite{aufiero_extended_2013}; Ashraf \emph{et al.}, 2018 \cite{ashraf_nuclear_2018} & fast \\
\hline
DIF3D \cite{derstine_dif3d:_1984} & Zhou \emph{et al.}, 2018 
\cite{zhou_fuel_2018} & thermal/ fast \\
\hline
MCODE/ORIGEN2 \cite{xu_mcode_2008,croff_users_1980}      & Ahmad \emph{et al.}, 
2015 \cite{ahmad_neutronics_2015}   & thermal  \\
\hline
\gls{MCNP}6/CINDER90 \cite{goorley_mcnp6_2013}     & Park \emph{et al.}, 2015; 
Jeong \emph{et al.}, 2016 \cite{park_whole_2015, jeong_equilibrium_2016}& 
thermal\\
\hline
SCALE/TRITON \cite{bowman_scale_2011,powers_new_2013}    & Powers \emph{et al.}, 
2014; Betzler \emph{et al.}, 2017 
\cite{powers_new_2013,powers_inventory_2014,betzler_molten_2017}& thermal/ fast\\
\hline
SERPENT2     & Rykhlevskii \emph{et al.}, 2017 \cite{rykhlevskii_online_2017} & 
thermal\\
\hline
\gls{MCNP}/REM  & Nuttin \emph{et al.} \cite{nuttin_potential_2005}&thermal  \\ 
\hline
\end{tabularx}
  \label{tab:fs_codes}
\end{table}
\FloatBarrier

@@

Aufiero \emph{et al.} extended the Monte Carlo burnup code SERPENT2 and 
employed it to study the material isotopic evolution of the 
\gls{MSFR}\cite{aufiero_extended_2013}. The 
developed extension directly accounts for the effects of online fuel 
reprocessing on depletion calculations and features a reactivity control 
algorithm. The extended version of SERPENT2 was assessed against a dedicated 
version of the deterministic ERANOS-based EQL3D procedure 
\cite{ruggieri_eranos_2006, fiorina_investigation_2013} and adopted to analyze 
the \gls{MSFR} fuel salt isotopic evolution.

We employed this extended SERPENT2 for a simplified unit-cell geometry of 
thermal spectrum thorium-fueled \gls{MSBR} and have had following problems: (1) 
lack of documentation describing how to use this built-in SERPENT2 online 
reprocessing capabilities\footnote{ Some challenges in no particular order: 
mass conservation is hard to achieve; not clear when use mflow card type 0, 1 or 2; 
difference between CRAM and TTA results; etc.} 
(Discussion forum for SERPENT users is only useful 
source of information at the moment); (2) reactivity control module described in Aufiero \emph{et al.} is 
not available in the latest SERPENT 2.1.30 release; (3) infinite multiplication 
factor behavior for simplified unit-cell model obtained using SERPENT2 built-in 
capabilities \cite{rykhlevskii_online_2017} does not match with exist MCNP6/Python-script
 results for the similar model by Jeong and Park\footnote{ In our 
study k$_{\infty}$ drops from 1.05 to 1.005 during a 1200 days of depletion simulation 
while in Jeong and Park work this parameter decreasing slowly from 1.065 to 1.05 for the 
similar time-frame.} \cite{jeong_equilibrium_2016}; (4) only few publication \cite{aufiero_extended_2013, 
ashraf_nuclear_2018} using these capabilities are available 
which is indicative of lack of reproducibility. Nevertheless, truly continuous 
online reprocessing capabilities of SERPENT2 is desirable feature for our 
future research. However, these capabilities should be carefully verified against 
ChemTriton/SCALE or proposed SaltProc/SERPENT2 package, and could be employed 
for removal of fission products with shorter residence time (e.g., Xe, Kr) which 
have a strong negative impact on core lifetime and breeding efficiency which 
we intent to do in the nearest future.

The present work introduces the online reprocessing simulation package, SaltProc, 
which expands the capability of the continuous-energy Monte Carlo Burnup 
calculation code, SERPENT2 \cite{leppanen_serpent_2015}, for simulation 
liquid-fueled \gls{MSR} operation 
\cite{rykhlevskii_arfc/saltproc:_2018}. It also reports the 
application of the coupled SaltProc-SERPENT2 system to the \gls{MSBR}, an 
extension of the work presented in 
\cite{rykhlevskii_full-core_2017, rykhlevskii_online_2017}. In this work, we 
analyzed \gls{MSBR} neutronics and fuel cycle to establish its equilibrium core 
composition. Additionally, we compared predicted operational and safety parameters of the \gls{MSBR} at 
both the initial and equilibrium states to characterize the evolution of its 
safety case over time. Finally, these simulations determined the appropriate $^{232}$Th feed rate  
for maintaining criticality and enabled analysis of the overall \gls{MSBR} fuel 
cycle performance.
